Supporting Information : Complex and informative dependencies propogate throughout ecology and can be revealed using copulas

### 2019-05-14 SupportingInformation.Rmd
more editing
adding auto link

Asymmetry of tail dependence was also verified by our nonparametric methods for
the other multivariate datasets. For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\Ps_l-\Ps_u$ were
$(-0.085,-0.041)$ for the leaf-curling plum aphid first flight data, 
indicating greater upper-tail dependence, and consistent with
<!--***DAN: Shya, pls make above results autolink-->
the results of Table \ref{MT-tab_multivar_summary} (row 9). 
For the *Ceratium furca* abundance data, confidence intervals were
$(0.011,0.044)$, indicating greater lower-tail dependence, and again
<!--***DAN: Shya, pls make above results autolink-->
consistent with the results of Table \ref{MT-tab_multivar_summary} (row 9).
For the methane-flux data, confidence intervals were 
$(-0.008,0.019)$.

>>>>

Asymmetry of tail dependence was also verified by our nonparametric methods for
the other multivariate datasets. For instance, the $95\%$ confidence intervals of the
mean over pairs of sampling locations of the statistic $\Ps_l-\Ps_u$ were 
(`r unname(round(stat_aphid_ff$numericdf[10,c(3,4)],3))`)
for the leaf-curling plum aphid first flight data, 
indicating greater upper-tail dependence, and consistent with
the results of Table \ref{MT-tab_multivar_summary} (row 9). 
For the *Ceratium furca* abundance data, confidence intervals were
(`r unname(round(stat_plankton_north_sea$numericdf[10,c(3,4)],3))`), 
indicating greater lower-tail dependence, and again 
consistent with the results of Table \ref{MT-tab_multivar_summary} (row 9).
For the methane-flux data, confidence intervals were 
(`r unname(round(stat_methane$numericdf[10,c(3,4)],3))`).
